\plaintitle

### 2016-09-21 drafts/labor/trackingWork.tex
incremental changes on complexity - still more to fix
MSB intro edits
pushing whatever i have...
remove flexibility. no flexibility!
moved a bunch of piecework history to its constituent sections. exciting!
added a ref shortname
piecework history of complexity revised
looked through complexity

\newlist{inlinelist}{enumerate*}{1}
\setlist*[inlinelist,1]{%
  label=\arabic*),
}

\setlist{nolistsep}
\def\plaintitle{Examining Crowd Work Through The Lens of Piecework}
\def\plainauthor{Ali Alkhatib, Margaret Levi, Michael Scott Bernstein}
\def\emptyauthor{}
\def\plainkeywords{Crowdsourcing; human computation; research vision}
\def\plaingeneralterms{Documentation, Standardization}

@@

% To make various LaTeX processors do the right thing with page size.
\def\pprw{8.5in}
\def\pprh{11in}
\special{papersize=\pprw,\pprh}
\setlength{\paperwidth}{\pprw}
\setlength{\paperheight}{\pprh}
\setlength{\pdfpagewidth}{\pprw}
\setlength{\pdfpageheight}{\pprh}
\definecolor{PineGreen}{HTML}{008800}
\definecolor{BrickRed}{HTML}{FF0000}
\definecolor{JokeGreen}{HTML}{00C953}
\newcommand{\msb}[1]{{\color{PineGreen}[MSB: #1]}}
\newcommand{\ali}[1]{{\color{BrickRed}[al2: #1]}}

@@

\newcommand{\subsubsubsection}[1]{\textit{#1}}
\newcommand{\pieceworkpers}{Piecework's perspective.}
\newcommand{\crowdworkpers}{Crowd work's perspective.}
\newcommand{\whatchanged}{What's different about crowd work.}
\newcommand{\implication}{Implications for crowd work research.}
\newcommand{\pieceworkdefinition}{piecework is the paradigm of renumeration that is largely made compelling for its use of
``payment for results''%
, leading to and leveraging narrower skill sets required for narrowly defined tasks,
and affording workers some amount of freedom to complete tasks
(and consequently earn money)
at at whatever rate and in whichever manner they wish}

@@

\category{H.5.m.}{Information Interfaces and Presentation
  (e.g. HCI)}{Miscellaneous} \category{See
  \url{http://acm.org/about/class/1998/} for the full list of ACM
  classifiers. This section is required.}{}{}

>>>>

\newlist{inlinelist}{enumerate*}{1}
\setlist*[inlinelist,1]{%
   % label=\alph*),
 label=\arabic*),
}

\setlist{nolistsep}
\def\plaintitle{Examining Crowd Work Through The Historical Lens of Piecework}
\def\plainauthor{Ali Alkhatib, Margaret Levi, Michael Scott Bernstein}
\def\emptyauthor{}
\def\plainkeywords{Crowdsourcing; on--demand labor; gig work}
\def\plaingeneralterms{Documentation, Standardization}

@@

% To make various LaTeX processors do the right thing with page size.
\def\pprw{8.5in}
\def\pprh{11in}
\special{papersize=\pprw,\pprh}
\setlength{\paperwidth}{\pprw}
\setlength{\paperheight}{\pprh}
\setlength{\pdfpagewidth}{\pprw}
\setlength{\pdfpageheight}{\pprh}
\definecolor{PineGreen}{HTML}{008800}
\definecolor{BrickRed}{HTML}{FF0000}
\definecolor{JokeGreen}{HTML}{00C953}
\newcommand{\msb}[1]{{\color{PineGreen}[MSB: #1]}}
\newcommand{\ali}[1]{{\color{BrickRed}[al2: #1]}}
\newcommand{\TO}{\textit{Turkopticon}}
\newcommand{\DO}{\textit{Dynamo}}

@@

\newcommand{\subsubsubsection}[1]{\textit{#1}}
\newcommand{\pieceworkpers}{Piecework's perspective}
\newcommand{\crowdworkpers}{Crowd work's perspective}
\newcommand{\whatchanged}{Comparing the phenomena}
\newcommand{\implication}{Implications for crowd work}
\newcommand{\pieceworkdefinition}{piecework is the paradigm of renumeration that is largely made compelling for its use of
``payment for results'',
leading to and leveraging narrower skill sets required for narrowly defined tasks,
and affording workers some amount of freedom to complete tasks
(and consequently earn money)
at at whatever rate and in whichever manner they wish} % do i use this more than once? even that much?

@@

\category{H.5.3.}{Information Interfaces and Presentation
  (e.g. HCI)}{Group and Organization Interfaces}
